Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-08-01 paper/Analisis.tex
Some typos

An ab-initio description of realistic rotation curves in simulations
depends on having access to the dynamic evolution the mass components
in the galaxy: stars, gas and dark matter. Such level of realism is
extremely complex to achieve, specially of one wants to get a
systematic description based on statistics of simulated objects.

@@

Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases with
rotational velocity. Continuous (dashed) lines connect the results for
homogeneous (central) source distribution. The line width increases
with rotational velocity up to factors of $\sim 2$ at $300$\kms with
respect to the static case. For the temperature $T=10^4$K used in our
radiative transfer calculations calculations the thermal velocity is
$v_{th}=12.8$\kms. For a model with $\tau_{H}$ it means that the
half-width can increase up to $350$\kms (at $V_{\rm max}=300$\kms)
compared to a half-width of $150$\kms in the static case.

@@

In order to gain a deeper understanding of these results we prepare 2D
histograms for the number of scatterings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
the results of such histogram in the case $\tau{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x-N_{\rm scatt}$. This Figure clearly support our hypothesis about
the photosphere in the homogeneous distribution, in this case most of
the photons that left with $x\sim 0$ have escaped with less than $10$
scatterings, clearly explaining the origin of a single central
peak. However, for a central distribution the situation is
different. In this case the number of scatterings remains high, on the
order of the optical depth, but the two peaks do get closer to each
other. In this situation each scattering leaves the photon closer to
the center of the line than the static case.

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{Neufeld.png}
 \label{fig:efvsNeufeld}\caption{Escape fraction as a function of the
   product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
   the infinite is slab shown as a continuous line. Different dashed
   lines correspond to different rotational velocities.}   
\end{figure}

>>>>

An ab-initio description of realistic rotation curves in simulations
depends on having access to the dynamic evolution the mass components
in the galaxy: stars, gas and dark matter. Such level of realism is
extremely complex to achieve, specially if one wants to get a
systematic description based on statistics of simulated objects.

@@

Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases with
rotational velocity. Continuous (dashed) lines connect the results for
homogeneous (central) source distribution. The line width increases
with rotational velocity up to factors of $\sim 2$ at $300$\kms with
respect to the static case. For the temperature $T=10^4$K used in our
radiative transfer calculations the thermal velocity is
$v_{th}=12.8$\kms. For a model with $\tau_{H}$ it means that the
half-width can increase up to $350$\kms (at $V_{\rm max}=300$\kms)
compared to a half-width of $150$\kms in the static case.

@@

In order to gain a deeper understanding of these results we prepare 2D
histograms for the number of scatterings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
the results of such histogram in the case $\tau_{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x-N_{\rm scatt}$. This Figure clearly support our hypothesis about
the photosphere in the homogeneous distribution, in this case most of
the photons that left with $x\sim 0$ have escaped with less than $10$
scatterings, clearly explaining the origin of a single central
peak. However, for a central distribution the situation is
different. In this case the number of scatterings remains high, on the
order of the optical depth, but the two peaks do get closer to each
other. In this situation each scattering leaves the photon closer to
the center of the line than the static case.

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{Neufeld.png}
 \caption{Escape fraction as a function of the
   product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
   the infinite is slab shown as a continuous line. Different dashed
   lines correspond to different rotational velocities.
   \label{fig:efvsNeufeld}}   
\end{figure}
